Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-03 paper.tex
Add placeholder comment on measuring output state

>>>>

Thanks to having padded the circuit with identity matrices at the end, if we measured $T>\frac{T}{2}$ on the time register, we would know that the other registers include the output of the required quantum computation. Now I would analyze the chances of getting this right, maybe in terms of fidelity or in terms of distance between this measured distribution and the ideal distribution...

\section{Conclusion}

This is a placeholder. Lorem ipsum...
